NEED TITLE

### 2015-06-10 ms.tex
expanded some details on the initialization and some of the numerical results

We use the adaptive mesh refinement code FLASH ver. 4.0.1 (Fryxell et al.
2000
; Dubey
et al.
2008
) to model isothermal, self-gravitating, hydrodynamic turbulence on isothermal gas with three-dimensional (3D),
periodic grids and 8 levels of refinement on a root grid of $128^3$, giving an effective resolution of $32K^3$.  
Self-gravity is computed with a multi-grid Poisson solver (see Ricker
2008), coupled with a fast-Fourier transform solution on the root grid. Similar to (Lee et. al Feb. 2015) our FLASH runs use the Harten-Lax-van Leer-Contact Riemann solver and an unsplit solver. ({\bf Lee et. al use Lee \& Deane (2009) do we?})

We start with a box with the physical length set to $L = 16$pc using periodic boundary condtions. The intial mass density is $\rho = 3x10^{-22}$ and the isothermal, ambient gas is set to a sound speed of $c_s = 2.64x10^{4}$ {\bf we also set $Mach_ambient = 5.0$ include?}. To initialize our simulations, we drive turbulence by applying a large scale ($1 \le kL \le 2$) solenoidal acceleration field as a momentum and energy source term. We apply this field in the absence of gravity and sink particle formation for 3 dynamical times until a statistical steady state is reached.
{\bf WHY JUST SOLENOIDAL}

@@

The gravitational force is computed differently than the gas. Sink particle-sink particle forces are computed via direct N-body calculation. While sink particle-gas and gas-sink particle is computed via the multi-grid Poisson solver.  As a result of these additional computations, two large scale gravity solutions must be found per timestep as oppose to one.  This allows to avoid the computationally expensive task of computing gas-sink particle forces via direct summation.

We have also implemented a new algorithm for mesh refinement in these simulations. As gas collapse under self gravity, certain regions rapidly increase in density. These regions are refined when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
%\frac{\rho}{\rho_0} = 45 \text{x} 4^{l} (\frac{N_{root}}{128})^2 (\frac{16\text{pc}}{L})^2 (\frac{c_s}{2.65x10^4 \text{cm s})^2 (\frac{3x10^{-22}\text{g cm^-3}}{\rho_0})
\label{eq:refinement_criteria}
\end{equation}
which when met causes the local grid to be refined by a factor of 2 provided that the maximum refinement level is not reached.

When the Truelove criterion is met at highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell.  This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution.  We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.
Our base grid's resolution of $128^3$ gives a cell length of $1.2 \text{x} 10^{-1}$pc which is sufficient to resolve the Jean's length
\begin{equation}
\lambda_J \equiv \sqrt{\frac{\pi c_{s}^2}{G \bar{\rho}}} \approx 3.5 \text{pc}
\end{equation}

@@

To initialize our simulation, we begin by applying solenoidal stirring forces to the uniform, periodic simulation volume at the root grid resolution of $128^3$ until statistical equilibrium is reached (approximately three crossing times).  After this equilibrium is established, we then apply self gravity, adaptive mesh refinement, and sink particle creation.  In Figure \ref{fig:entire projection} we show a projection along the x-axis of the entire simulation volume that has up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. Regions that are highly refined are the densest regions which are smoother than the low-density more pixelated regions.
\begin{figure}
\plotone{movieframe_quad2_0498.png}
\caption{Projection of the density along the z-axis of the entire simulation volume. The root grid is $128^3$ with up to 8 levels of refinement, giving an effective resolution of $32\,{\rm K}^3$. This snapshot is taken $2.8$Myr after star formation is turned on. \label{fig:entire projection}}
\end{figure}

@@

At the instance in time shown in Figure \ref{fig:entire projection}, a total of five star particles have been formed.  However, these star particles are not formed in isolation.  Rather they congregate in two star forming regions shown in Figure \ref{fig:star forming regions}.  In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center.  Visually, the character of accretion at the this outer scale appear to flow along filaments, though previous work (Lee et al. 2014) has shown that the majority of accretion is spherical.  We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}

>>>>

We use the adaptive mesh refinement code FLASH ver. 4.0.1 (Fryxell et al. 
2000
; Dubey
et al.
2008
) to model isothermal, self-gravitating, hydrodynamic turbulence on isothermal gas with three-dimensional (3D),
periodic grids and 8 levels of refinement on a root grid of $128^3$, giving an effective resolution of $32K^3$.  
Self-gravity is computed with a multi-grid Poisson solver (see Ricker 2008), coupled with a fast-Fourier transform solution on the root grid. Similar to (Lee et. al Feb. 2015) our FLASH runs use the Harten-Lax-van Leer-Contact Riemann solver and an unsplit solver. (Lee \& Deane (2009)

We start with a box with the physical length set to $L = 16$pc using periodic boundary condtions. The intial mass density is $\rho = 3x10^{-22}$ and the isothermal, ambient gas is set to a sound speed of $c_s = 2.64x10^{4}$. To initialize our simulations, we drive turbulence by applying a large scale ($1 \le kL \le 2$) solenoidal acceleration field as a momentum and energy source term. We apply this field in the absence of gravity and sink particle formation for 3 dynamical times until a statistical steady state is reached.
{\bf WHY JUST SOLENOIDAL}

@@

The gravitational force is computed differently between sink particles than between sink particles and the gas. Sink particle-sink particle forces are computed via direct N-body calculation. While sink particle-gas and gas-sink particle is computed via the multi-grid Poisson solver. As a result of these additional computations, two large scale gravity solutions must be found per timestep as oppose to one. This allows to avoid the computationally expensive task of computing gas-sink particle forces via direct summation.

We have also implemented a new algorithm for mesh refinement in these simulations. As gas collapse under self gravity, certain regions rapidly increase in density. These regions are refined when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
\frac{\rho}{\rho_{0}} = 45 \cdot 4^{l} \left( \frac{N_{root}}{128} \right)^2 \left( \frac{16 \text{pc}}{L} \right)^2 \left( \frac{c_{s}}{2.65\text{x}10^4 \text{cm s$^{-1}$}} \right)^2 \left( \frac{3 \text{x}10^{-22} \text{g cm$^{-3}$}}{\rho_{0}} \right)
\label{eq:refinement_criteria}
\end{equation}
 where $l$ is the refinement level, with $l = 0$ corresponding to the root grid. When this density condition is met the local grid is refined by a factor of 2 provided that the maximum refinement level has not reached. 
We reach a maximum of $\rho / \rho_{0} \approx 3 \text{x} 10^{7}$ at $l$ = 8, the maximum refinement level. Thus we traverse nearly 8 orders of magnitude in the density in our AMR simulations.
When the Truelove criterion is met at the highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell. This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution. We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.
Our base grid's resolution of $128^3$ gives a cell length of $1.2 \text{x} 10^{-1}$pc which is sufficient to resolve the Jean's length
\begin{equation}
\lambda_J \equiv \sqrt{\frac{\pi c_{s}^2}{G \bar{\rho}}} \approx 3.5 \text{pc}
\end{equation}

@@

To initialize our simulation, we begin by applying solenoidal stirring forces to the uniform, periodic simulation volume at the root grid resolution of $128^3$ until statistical equilibrium is reached (approximately three crossing times). After this equilibrium is established, we then apply self gravity, adaptive mesh refinement, and sink particle creation. In Figure \ref{fig:entire projection} we show a projection along the z-axis of the entire simulation volume that has up to 8 levels of refinement, giving an effective resolution of $32\,{\rm K}^3$. Regions that are highly refined are the densest regions which are smoother than the low-density more pixelated regions.
\begin{figure}
\plotone{movieframe_quad2_0498.png}
\caption{Projection of the density along the z-axis of the entire simulation volume. The root grid is $128^3$ with up to 8 levels of refinement, giving an effective resolution of $32\,{\rm K}^3$. This snapshot is taken $2.8$Myr after star formation is turned on. \label{fig:entire projection}}
\end{figure}

@@

At the instance in time shown in Figure \ref{fig:entire projection}, a total of 20 star particles have been formed. A couple of these star particles are formed in isolation though the majority formed in binaries and there is a ring of ten in one region. They congregated in several star forming regions shown in Figure \ref{fig:star forming regions}. In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center. Visually, the character of accretion at the this outer scale appear to flow along filaments, though previous work (Lee et al. 2014) has shown that the majority of accretion is spherical. We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}
